### 2012-04-21 docs/getting_started/getting_started.tex
detail string version of BCs

@@

\item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, 
      {\tt bcx\_hi }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary
   condition types at the lower (`{\tt lo}') and upper (`{\tt hi}')
   domain boundaries in the $x$, $y$, and $z$ coordinate directions.
   The different types are set via integer flags listed in table~\ref{arch:table:bcflags}.

   \begin{table}[h]
   \caption{\label{arch:table:bcflags} Boundary condition flags}  
   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & $-1$ \\
   inlet (user-defined) & $11$ \\
   outlet               & $12$ \\
   symmetry             & $13$ \\
   slip wall            & $14$ \\
   no-slip wall         & $15$ \\
   \hline
   \end{tabular}
   \end{center}
   \end{table}

>>>>

{\bf Note: unless otherwise specified all quantities in \maestro\ are
assumed to be in CGS units.}

@@

\item There are two ways to specify boundary conditions---via integer flags
      or descriptive string names.  If the string names are present,
      then they will override the integer quantities in determining
      the boundary conditions.

   \begin{itemize}

   \item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, {\tt bcx\_hi
      }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary condition
      types at the lower (`{\tt lo}') and upper (`{\tt hi}') domain
      boundaries in the $x$, $y$, and $z$ coordinate directions.  The
      different types are set via integer flags listed in
      table~\ref{gs:table:bcflags}.

   \begin{table}[h]
   \caption{\label{gs:table:bcflags} Boundary condition flags}  
   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & $-1$ \\
   inlet (user-defined) & $11$ \\
   outlet               & $12$ \\
   symmetry             & $13$ \\
   slip wall            & $14$ \\
   no-slip wall         & $15$ \\
   \hline
   \end{tabular}
   \end{center}
   \end{table}

   \item {\tt xlo\_boundary\_type}, {\tt ylo\_boundary\_type}, {\tt
   zlo\_boundary\_type}, {\tt xhi\_boundary\_type}, {\tt
   yhi\_boundary\_type}, {\tt zhi\_boundary\_type} are the boundary
   condition types at the lower and upper domain boundaries in 
   the $x$, $y$, and $z$ coordinate directions.   The boundary
   type is set by providing a string name---valid values are listed
   in table~\ref{gs:table:bcstrings}

   \begin{table}[h]
   \caption{\label{gs:table:bcstrings} Boundary condition string names}  
   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & ``periodic'' \\
   inlet (user-defined) & ``inlet'' \\
   outlet               & ``outlet'' \\
   symmetry             & ``symmetry'' \\
   slip wall            & ``slip wall'' \\
   no-slip wall         & ``no slip wall'' \\
   \hline
   \end{tabular}
   \end{center}
   \end{table}

  The string-based parameters are a newer option for specifying
  boundary conditions, and are preferred due to clarity.  The
  conversion between the string names and integer flags is done
  by \boxlib\ in the {\tt bc\_module} at the time of initializing
  the runtime parameters.
